### 2022-09-01 sections/experience.tex
LPPL v1.3c
Update experience.tex

\begin{cventries}
\cventry
{Instructor Professor} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2019 - on leave}
{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}

\cventry
{Adjunct Professor} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2014 - 2018}
{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}

@@

\cventry
{Lecturer} 
{Universidad de Chile} 
{Santiago, Chile} 
{2013 - 2016}
{School of Government and Public Management, Institute of Public Affairs}\vspace{1.5mm}

\end{cventries}

>>>>

\begin{cventries}
\cventry
{Lecturer} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2014 - 2019}
{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}

@@

\cventry
{Lecturer} 
{Universidad de Chile} 
{Santiago, Chile} 
{2013 - 2016}
{School of Government and Public Management, Institute of Public Affairs}\vspace{1.5mm}
\end{cventries}
\pagebreak
